A Study on Common Bug Fix Patterns in Rust

### 2022-10-29 main.tex
more explicit about goal

Yet, to the best of our knowledge, no research has sought to identify the most pervasive bug fix patterns within Rust programs. In this project, using a novel program modelling method, we mined the top 18 most-starred Rust projects in Github to discover the most common bug fix patterns committed to their repositories. We analyzed 87,726 code changes drawn from 57,214 commits across these 18 projects. After clustering the code changes, and conducting a manual analysis, we discovered 19 groups of cross-project bug fix patterns, which we categorize as (1) general patterns and (2) borrow-checker-related patterns. We describe each of these patterns and their implications to automated program repair.
\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
\subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

>>>>

Yet, to the best of our knowledge, no research has sought to identify the most pervasive bug fix patterns within Rust programs. In this project, we developed a novel embedding of Rust code into fixed-sized vectors. Using this embedding, we mined the top 18 most-starred Rust projects in Github to discover the most common bug fix patterns committed to their repositories. We analyzed 87,726 code changes drawn from 57,214 commits across these 18 projects. After clustering the code changes, and conducting a manual analysis, we discovered 19 groups of cross-project bug fix patterns, which we categorize as (1) general patterns and (2) borrow-checker-related patterns. We describe each of these patterns and their implications to automated program repair.
\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
\subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

### 2022-10-29 sections/introduction.tex
more explicit about goal

Bugs have long been an unavoidable part of computer programming, predating Grace Hopper's literal debugging session in 1947; even today, bug-free software remains an aspirational goal for software engineering research. One step towards that goal has been studying common bug patterns (and their corresponding fixes) across multiple software systems. Research efforts categorizing common bug patterns date back to at least 1975, where Endres tried to categorize bug patterns in operating system implementations~\cite{endres1975analysis}.

In this work, we empirically analyze the most popular Rust projects in GitHub, aiming to discover common bug patterns that afflict these projects. Our interest comes from a desire to develop automated program repair tools, but we believe these insights can also be of broader service. Automated program repair~\cite{goues2019automated,liu2018survey} tools try to find bug locations in the source code (using a fault localization module) and then generate patches to fix them, possibly without human intervention, so that the modified program meets desired specifications (implicit or explicit). A powerful automated program repair system has many useful applications and could significantly simplify debugging, thus reducing software development cost~\cite{le2012systematic}. A set of common bug fix patterns can be a useful input to an APR system: it tells how to fix recurring buggy structures, thus reducing the search space for patch generation~\cite{jeffrey2009bugfix}.

>>>>

Bugs have long been an unavoidable part of computer programming, predating Grace Hopper's literal debugging session in 1947; even today, bug-free software remains an aspirational aim for software engineering research. One step towards that aim has been studying common bug patterns (and their corresponding fixes) across multiple software systems. Research efforts categorizing common bug patterns date back to at least 1975, where Endres tried to categorize bug patterns in operating system implementations~\cite{endres1975analysis}.

In this work, we empirically analyze the most popular Rust projects in GitHub. Our goal is to discover common bug patterns that afflict these projects. Although we are motivated by a desire to develop automated program repair tools, we believe these insights can also be of broader service. Automated program repair~\cite{goues2019automated,liu2018survey} tools try to find bug locations in the source code (using a fault localization module) and then generate patches to fix them, possibly without human intervention, so that the modified program meets desired specifications (implicit or explicit). A powerful automated program repair system has many useful applications and could significantly simplify debugging, thus reducing software development cost~\cite{le2012systematic}. A set of common bug fix patterns can be a useful input to an APR system: it tells how to fix recurring buggy structures, thus reducing the search space for patch generation~\cite{jeffrey2009bugfix}.
